---
title: "School Report"
author: "Education Dashboard | PHA Data Team "
output: html_document
always_allow_html: true
params:
  SchoolID: NA
  school: NA
  schoolCases: NA
  rendered_by_shiny: FALSE
---

```{r Load in packages and data, echo=FALSE, message=FALSE, error=FALSE, warning=FALSE, include=FALSE}
# The `params` object is available in the document.
knitr::opts_chunk$set(echo = TRUE, fig.width = 10)

#read in the params defined in the shiny app
SchoolID <- params$SchoolID
school <- params$school
schoolCases <- params$schoolCases
#postcodes <- params$postcodes

```
---

#### Summary: **`r as.character(SchoolID)`** - **`r as.character(school$InstitutionName)`**  
#### As of: **`r Sys.Date()`**

---

**NOTE: This Report Is For Internal Use Only**

---

#### Key Details:

---

ID: **`r as.character(SchoolID)`**  
Name: **`r as.character(school$InstitutionName)`**  
Earliest Sample: **`r as.character.Date(school$EarliestSample)`**  
Post Code: **`r as.character(school$Postcode)`**  
LGD: **`r as.character(school$LGDName)`**  


---


---

Total Cases on Dynamics: **`r as.character(school()$TotalCases)`**  
Total Possible Close Contacts: **`r as.character(school()$TotalCloseContacts)`**  

---

#### Epicurve:

---

This epicurve has been generated using the Date Of Positive Sample.  
Cases are broken down into known and unknown strains.

```{r epicurve, echo=FALSE, message=FALSE, error=FALSE, warning=FALSE} 
epidata <- schoolCases %>%
  dplyr::select(CaseNumber, DateOfSample, WgsVariant) %>%
  dplyr::mutate(WgsVariant = ifelse(is.na(WgsVariant), 'Unknown', WgsVariant))

name <- school$InstitutionName

date_range <- lubridate::date(epidata$DateOfSample)

day_span <- length(unique(lubridate::day(date_range)))

week_span <- length(unique(lubridate::week(date_range)))

month_span <- length(unique(months(date_range)))

ggplot2::ggplot(epidata) +
  ggplot2::geom_histogram(
    ggplot2::aes(x = as.Date(DateOfSample), fill = WgsVariant),
    binwidth = 1,
    alpha = 0.9,
    color = "grey"
  ) +
  ggplot2::geom_text(
    stat = "count",
    size = 3.5,
    ggplot2::aes(x = as.Date(DateOfSample), label = ..count..),
    nudge_y = 0.25
  ) +
  ggplot2::labs(
    title = paste("Epicurve for", name),
    x = "Date of Sample",
    y = "Cases",
    fill = "Variant Type"
  ) +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1)) +
  ggplot2::theme_bw() +
  if (month_span == 1) {
    ggplot2::scale_x_date(breaks = scales::breaks_width("1 day"),
                          labels = scales::date_format("%d-%m-%Y"))
  } else if (month_span == 2) {
    ggplot2::scale_x_date(breaks = scales::breaks_width("7 days"),
                          labels = scales::date_format("%d-%m-%Y"))
  } else if (month_span >= 3) {
    ggplot2::scale_x_date(breaks = scales::breaks_width("1 months"),
                          labels = scales::date_format("%b-%Y"))
  }
```

---

#### Demographics:

---

School Years
```{r year, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}

name <- school$InstitutionName[1]

school.year.table <- schoolCases %>%
  dplyr::select(CaseNumber,
                Gender,
                SchoolYear)

ggplot2::ggplot(data = school.year.table, ggplot2::aes(x = SchoolYear, fill = Gender)) +
  ggplot2::geom_bar(data = subset(school.year.table, Gender == "Female")) +
  ggplot2::geom_bar(data = subset(school.year.table, Gender == "Male"),
                    ggplot2::aes(y = ..count.. * (-1))) +
  ggplot2::coord_flip() +
  ggplot2::scale_x_discrete(drop = FALSE) +
  ggplot2::labs(
    title = paste("Case Frequencies for", name),
    x = "School Group",
    y = "Frequency",
    fill = "Gender"
  ) +
  ggplot2::theme_bw()
```


School Year Attack Rate
```{r AR, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}


name <- school$InstitutionName



attack.rate.table <- school %>%
  dplyr::select(
    AttackRateNursery,
    AttackRateReception,
    AttackRateY1,
    AttackRateY2,
    AttackRateY3,
    AttackRateY4,
    AttackRateY5,
    AttackRateY6,
    AttackRateY7,
    AttackRateY8,
    AttackRateY9,
    AttackRateY10,
    AttackRateY11,
    AttackRateY12,
    AttackRateY13,
    AttackRateY14,
    AttackRateSN
  ) %>%
  dplyr::rename(
    Nursery = AttackRateNursery,
    Reception = AttackRateReception,
    Primary1 = AttackRateY1,
    Primary2 = AttackRateY2,
    Primary3 = AttackRateY3,
    Primary4 = AttackRateY4,
    Primary5 = AttackRateY5,
    Primary6 = AttackRateY6,
    Primary7 = AttackRateY7,
    Year8 = AttackRateY8,
    Year9 = AttackRateY9,
    Year10 = AttackRateY10,
    Year11 = AttackRateY11,
    Year12 = AttackRateY12,
    Year13 = AttackRateY13,
    Year14 = AttackRateY14
  ) %>%
  tidyr::pivot_longer(cols = everything(),
                      names_to = "AttackRate",
                      values_to = "count") %>%
  dplyr::mutate(AttackRate = factor(
    AttackRate,
    levels = c(
      "Nursery",
      "Reception",
      "Primary1",
      "Primary2",
      "Primary3",
      "Primary4",
      "Primary5",
      "Primary6",
      "Primary7",
      "Year8",
      "Year9",
      "Year10",
      "Year11",
      "Year12",
      "Year13",
      "Year14"
    )
  ))

ggplot2::ggplot(data = attack.rate.table, ggplot2::aes(AttackRate, count)) +
  ggplot2::geom_bar(stat = "identity", fill = "#408cbc") +
  ggplot2::scale_x_discrete(drop = FALSE) +
  ggplot2::coord_flip() +
  ggplot2::labs(
    title = paste("Attack Rates per Year for", name),
    x = "School Year",
    y = "28 Day Attack Rate (%)"
  ) +
  ggplot2::scale_y_continuous(limits = c(0, 100), n.breaks = 10) +
  ggplot2::theme_bw()
```

```{r old_demo, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}

# #modified code from Stephen Morgan's Cluster IMT App
# #----
# age_sex_cases <- schoolCases %>%
#   dplyr::select(AgeAtPositiveResultSC, Gender, CaseNumber)
# 
# age_sex_male <- age_sex_cases %>%
#   dplyr::filter(Gender == "Male")
# 
# age_sex_female <- age_sex_cases %>%
#   dplyr::filter(Gender == "Female")
# 
# br = c(0, 5, 10, 20, 30, 40, 50, 60, 70, 200)
# 
# ranges = c("<5",
#            "5-9",
#            "10-19",
#            "20-29",
#            "30-39",
#            "40-49",
#            "50-59",
#            "60-69",
#            "70+")
# 
# freq_male <-
#   hist(
#     age_sex_male$AgeAtPositiveResultSC,
#     breaks = br,
#     include.lowest = TRUE,
#     plot = FALSE
#   )
# 
# freq_female <-
#   hist(
#     age_sex_female$AgeAtPositiveResultSC,
#     breaks = br,
#     include.lowest = TRUE,
#     plot = FALSE
#   )
# 
# 
# male_data <-
#   data.frame(range = ranges, frequency = freq_male$counts)
# 
# female_data <-
#   data.frame(range = ranges, frequency = freq_female$counts)
# 
# female_data <- female_data %>%
#   dplyr::mutate(Gender = "Female")
# 
# male_data <- male_data %>%
#   dplyr::mutate(frequency = frequency * -1,
#                 Gender = "Male")
# 
# both_data <- rbind(female_data, male_data)
# 
# both_data <- as.data.frame(both_data)
# 
# ggplot2::ggplot(both_data, ggplot2::aes(x = range, y = frequency, fill = Gender)) +
#   ggplot2::geom_bar(stat = "identity", position = "identity") +
#   ggplot2::scale_x_discrete(
#     name = "Age Bins",
#     limits = c(
#       "<5",
#       "5-9",
#       "10-19",
#       "20-29",
#       "30-39",
#       "40-49",
#       "50-59",
#       "60-69",
#       "70+"
#     )
#   ) +
#   ggplot2::scale_y_continuous(
#     name = "Frequency",
#     breaks = pretty(both_data$frequency),
#     labels = abs(pretty(both_data$frequency))
#   ) +
#   ggplot2::ggtitle("Case Age by Gender") +
#   ggplot2::coord_flip() +
#   ggplot2::geom_hline(yintercept = 0) +
#   ggplot2::theme_bw()
#----
    
```


```{r map, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}
# 
# #define the cluster data
# #map_data <- clusterCases
#                 
# #filter table to contain only postcode lat and long
# #lat_and_long <- postcodes %>%
#            # filter(postcode == cluster$Postcode) %>%
#            # select(postcode, longitude, latitude)
# 
# #define cluster lat and long
# cluster_lat <- cluster$latitude
# cluster_long <- cluster$longitude
#                 
# #define default zoom level of map
# ZoomLevel = 9
#     
# #define custom markers or leaflet for cases and for cluster source
# case_icon <- makeAwesomeIcon(
#   icon = "glyphicon glyphicon-user", 
#   library = "glyphicon", 
#   markerColor = "lightblue", 
#   iconColor = "white", 
#   squareMarker = TRUE,
#   spin = FALSE)
# 
# source_icon <- makeAwesomeIcon(
#   icon = "glyphicon glyphicon-pushpin", 
#   library = "glyphicon", 
#   markerColor = "lightred", 
#   iconColor = "white", 
#   squareMarker = TRUE,
#   spin = FALSE)
#             
# #define the leaflet map
# #doesnt include lgd or ward due to memory issue
# map <- leaflet() %>%
#   addTiles() %>%
#   addAwesomeMarkers(data = clusterCases,
#                     lat = clusterCases$Latitude, 
#                     lng = clusterCases$Longitude, 
#                     icon = case_icon, 
#                     popup = paste0(
#                         "<strong>Case ID: </strong>", clusterCases$CaseNumber, "<br>",
#                         "<strong>Postcode: </strong>", clusterCases$PostCode, "<br>",
#                         "<strong>Date of Sample: </strong>", clusterCases$DateOfSample, "<br>"
#                     ),
#                     group = "Cluster Cases") %>%
#   addAwesomeMarkers(data = cluster,
#                     lat = cluster$latitude, 
#                     lng = cluster$longitude, 
#                     icon = source_icon,
#                     popup = paste0(
#                         "<strong>Cluster Name: </strong>", cluster$ClusterName,"<br>",
#                         "<strong>HPZoneID: </strong>", cluster$ClusterID,"<br>",
#                         "<strong>Postcode: </strong>", cluster$Postcode,"<br>",
#                         "<strong>Setting: </strong>", cluster$ClusterSetting,"<br>"
#                     ),
#                     group = "Cluster Source") %>%
#   setView(lat = cluster_lat, lng = cluster_long, zoom = ZoomLevel) %>%
#   addLayersControl(overlayGroups = c("Cluster Cases","Cluster Source"),
#                    options = layersControlOptions(collapsed = FALSE))
# 
# #output leaflet map to report              
# map

```
